The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-06 paper_draft.Rmd
working on the variables table

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valley = case_when(dept == "Chuquisaca", "Cochabamba", "Tarija" ~ 1,
                            dept != "Chuquisaca", "Cochabamba", "Tarija" ~ 0))

@@

```
\begin{table}
\centering
\caption{Variable definitions}
\label{variableDefinitions}
\begin{tabular}{ll}
\hline
\hline
Variable name      & Description                                   \\
\hline
svr\_mean          & Monthly mean of SVR at a park                 \\
svr\_median        & Monthly median of SVR at a park               \\
svr\_p10           & Monthly 10th percentile of SVR at a park      \\
svr\_p25           & Monthly 25th percentile of SVR at a park      \\
svr\_p75           & Monthly 75th percentile of SVR at a park      \\
svr\_p90           & Monthly 90th percentile of SVR at a park      \\
recreation\_visits & Monthly number of recreation visits at a park \\
\hline
\end{tabular}
\end{table}

>>>>

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valley = case_when(dept %in% c("Chuquisaca", "Cochahamba", "Tarija") ~ 1, TRUE ~ 0),
         mountain = case_when(dept %in% c("La Paz", "Oruro", "Potosi") ~ 1, TRUE ~ 0),
         plains = case_when(dept %in% c("Beni", "Pando", "Santa Cruz") ~ 1, TRUE ~ 0),
         lagged_flood =

@@

```
\begin{table}
\centering
\caption{Variable definitions}
\label{variableDefinitions}
\begin{tabular}{ll}
\hline
\hline
Variable name      & Description                                               \\
\hline
Attend          & Binary variable, 1 = attends school                          \\
Register        & Binary variable, 1 = registered for school                   \\
Work_reason     & Binary variable, 1 = does not attend school for work reasons \\
Lny             & Log of income per capita (in Bolivianos/month)
Female          & Binary variable, 1 = female      \\
Age             & Age in years       \\
Child           & 
Grandchild
Num_children
Secondary
hhhead_educ
female_hhhead
Floods          & Number of flood occurrences per dept per year      \\
Droughts        & Number of drought occurrences per dept per year \\
Dept
Valleys
Mountains
Plains

\hline
\end{tabular}
\end{table}
